A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-07-27 Manuscript/vaught_2017.tex

\begin{abstract}

The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. These observations probe unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended emission around any of the sample galaxies, thus placing strong upper limits on the brightness of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc. The imaging also resolves the \ion{Mg}{2} observed galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds. Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.

\end{abstract}

@@

\hline 
\end{tabular}
\label{tab:prop}
\end{table*}

@@

Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs. SFR. The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and thus the possibility to detect higher SB of values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$. Figure \ref{fig:detection_lim} shows the same SB values as Figure \ref{fig:SFR_lim} vs $\log(M_*/M_{\odot})$. The figure is suggestive that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$.

@@

>>>>

\begin{abstract}
%The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies. One way to better constrain these %parameters is to measure the spatial extent of the outflow in emission. 
We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.   The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
%Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds. Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.
\end{abstract}

@@

\hline 
\end{tabular}
\begin{tablenotes}
\small
\item The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' spectral energy distributions with Magphys \citep{duCunha2008} as described in \citet{Rubin_2014}.
\end{tablenotes}
\label{tab:prop}
\end{table*}

@@

Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs. SFR. The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
%to detect higher SB values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$. 
Figure \ref{fig:detection_lim} shows the same SB values as in Figure \ref{fig:SFR_lim} vs. $\log(M_*/M_{\odot})$. The figure suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.  Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$.  If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\acknowledgements

K.H.R.R. acknowledges support from the Alexander von Humboldt foundation in the context of the Humboldt Postdoctoral Fellowship.  The Humboldt foundation is funded by the German Federal Ministry for Education and Research.

These findings are in part based on observations collected at the
European Organisation for Astronomical Research in the Southern
Hemisphere under ESO programs 090.A-0427(A).
